Scalar Parametrization for Joint Time-Frequency interpolation in a MIMO-OFDM channel

### 2019-10-09 paper/main.tex
modified

\begin{figure} 
\includegraphics[width=0.45\textwidth]{images/new-adpm-crop.pdf} 
\caption{Subcarriers which need to be quantized} 
\label{ber_overvie}
\vspace{-5pt} 
\end{figure}

@@

\begin{equation} 
\Delta_{n} = \begin{cases} 
    M \Delta_{n-1}, & \text{if $\beta_{n} = \beta_{n-1}$}.\\ 
    \Delta_{n-1}/m , & \text{if $\beta_{n} \neq \beta_{n-1}$}. 
  \end{cases} 
\end{equation}

@@

Now here we can see the advantage of using subcarriers in an alternating fashion as given in the Section~\ref{section1}. With this method we could exploit both time and frequency correlation because

@@

Initialization is performed by using $10\times12$ bits for each subcarrier for the initial two time frames. Later, the quantization will take place in the time-domain using one bit for each parameter. Since the bit budget is low and we are considering slowly varying channels, therefore, we will be sending either theta or phi parameters alternatingly in the time domain while keeping the unsent parameters equal to their previous values. This brings down the bit budget to 6 bits average per fed back subcarrier.

Describing how you performed ADPCM to carry out the 1-bit quantization. Also, the increment rate was 2.4 times the decay rate. Also, need to describe the initialization of the Delta values required in the quantization process. I need to cite that paper. We should also try over different quantization rates to compare \cite{Gupt1905:Predictive}

>>>>

\begin{figure}
\label{adpm-fig}
\includegraphics[width=0.45\textwidth]{images/new-adpm-crop.pdf} 
\caption{Subcarriers which need to be quantized} 
\label{ber_overvie}
\vspace{-5pt} 
\end{figure}

@@

\begin{equation}
\label{delta_eqn}
\Delta_{n} = \begin{cases} 
    M \Delta_{n-1}, & \text{if $\beta_{n} = \beta_{n-1}$}.\\ 
    \Delta_{n-1}/m , & \text{if $\beta_{n} \neq \beta_{n-1}$}. 
  \end{cases} 
\end{equation}

@@

Now here we can see the advantage of using subcarriers in an alternating fashion as given in the previous section. With this method we could exploit both time and frequency correlation because

@@

Initialization is performed by using $10\times12$ bits for each subcarrier for the initial two time frames. Later, the quantization will take place in the time-domain using one bit for each parameter. Since the bit budget is low and we are considering slowly varying channels, therefore, either theta or phi parameters are sent alternatingly in the time domain while keeping the unsent parameters equal to their previous values as show in the Figure \ref{adpm-fig}. Here $\Theta$ is the the collection of all $\theta$'s and $\Phi$ is the collection of all $phi$'s. This brings down the bit budget to average of 5(Size of $\Theta$) and 7(Size of $\Phi$) i.e. 6 bits average per fed back subcarrier.

\bf{ADPM Design}: The decrement rate - \bm is 2.4 times the \bM - increment rate in the Equation~\ref{delta_eqn} . This ratio was decided after trying with different ratios. This implies that if quantied values loose track of the actual values then after changing delta quickly they start following it again.
Also, need to describe the initialization of the Delta values required in the quantization process. Need to cite that paper. We should also try over different quantization rates to compare
